Flexible Scientific Data Management for Plant Phenomics Research

### 2013-03-11 s4biodiv2013/PODD-S4BIODIV-Submission.tex
fix tex syntax so it compiles
add figures to pdf

@@

%Affiliation:
\institution{
      eResearch Group, School of Information Technology and Electronic Engineering,
             University of Queensland, Brisbane, Australia
 \and CSIRO Plant industry, High Resolution Plant Phenomics Centre, Canberra, Australia
 \and CSIRO IMT Advanced Scientific Computing and Research Data Services, Melbourne, Australia}

@@

Figure 1. HRPPC component relationships and data flow

@@

The parent object types and properties used by PODD to establish basic ground
rules for rendering and validation are defined in a small base schema ontology.
General scientific properties and phenotype specific properties are then defined
in larger extension ontologies as illustrated in Figure 2.

%%% FIXME: TODO: Insert Figure 2 here

Figure 2. PODD schema ontology hierarchy

>>>>

\usepackage{graphicx}

@@

%Affiliation:
\institute{
      eResearch Group, School of Information Technology and Electronic Engineering,
             University of Queensland, Brisbane, Australia
 \and CSIRO Plant industry, High Resolution Plant Phenomics Centre, Canberra, Australia
 \and CSIRO IMT Advanced Scientific Computing and Research Data Services, Melbourne, Australia}

\maketitle

@@

%%Figure 1. HRPPC component relationships and data flow
\begin{figure}
\begin{center}
 \includegraphics[width=12cm,keepaspectratio=true]{plantscan-workflow-figure1.png}
 % plantscan-workflow-figure1.png: 598x330 pixel, 72dpi, 21.10x11.64 cm, bb=0 0 598 330

\caption{HRPPC component relationships and data flow}
\label{hrppccomponents}
\end{center}
\end{figure}

@@

The parent object types and properties used by PODD to establish basic ground
rules for rendering and validation are defined in a small base schema ontology.
General scientific properties and phenotype specific properties are then defined
in larger extension ontologies as illustrated in Figure~\ref{poddontologies}.

%Figure 2. 
\begin{figure}
\begin{center}
 \includegraphics[width=12cm,keepaspectratio=true]{podd-ontologies-figure2.png}
 % podd-ontologies-figure2.png: 5097x2360 pixel, 600dpi, 21.58x9.99 cm, bb=0 0 612 283

\caption{PODD ontology hierarchy}
\label{poddontologies}
\end{center}
\end{figure}
